\begin{rubric}{Activities}
\entry*[]%
\textbf{Member of the Educational Council, NORA\hfill\textit{2023 -- present}} \par 
Contributed to shaping the educational strategies and initiatives in AI across Norway as part of NORA's educational council. Played a key role in driving forward the agenda of integrating AI into broader educational frameworks nationally.
% 
\entry*[]%
\textbf{Challenge Organizer, Various International Workshops\hfill\textit{2018 -- present}} \par
Organized and led multiple challenges across renowned workshops such as ACM MultiMedia, ICPR, ImageCLEF, DLAMC, ICMR, and Nordic AI Meet. Developed challenge themes, managed participant outreach, submission evaluation, and ensured smooth operation of challenge sessions.
%
\entry*[]%
\textbf{Main Organizing Committee Member, MediaEval\hfill\textit{2018 -- present}} \par
Actively involved in the central organization of MediaEval, an annual international multimedia workshop. Responsible for overseeing key aspects of the workshop, including program planning, speaker coordination, and participant engagement.
% 
\entry*[]%
\textbf{Technical Program Committee Member, Various International Workshops\hfill\textit{2018 -- present}} \par
Actively involved in the technical program committees for several high-profile conferences, including: ACM MM, ACM MM Asia, CBMS, ISMICT, MultiMediaEval, ICME, Nature Scientific Reports, and Nature Scientific Data.
%
\entry*[]%
\textbf{Conference Organizer, Norwegian Artificial Intelligence Society (NAIS)\hfill\textit{2022}} \par
Contributed to organizing NAIS's annual conference, focusing on advancing and showcasing the latest developments in artificial intelligence in Norway.
%
\entry*[]%
\textbf{Editor, SIGMM Records\hfill\textit{2019 -- 2023}} \par
Served as an editor for SIGMM Records, responsible for the interview section.
%
\entry*[]%
\textbf{Journal Club Coordinator, OsloMet AI Club\hfill\textit{2019 -- 2020}} \par
Initiated and coordinated a bi-weekly journal club for the AI Lab at OsloMet. Facilitated discussions on recent advancements and research in AI, promoting a culture of continuous learning and academic discourse.
\end{rubric}