\begin{rubric}{Experience}
%
\entry*[2021 -- present]%
\textbf{Research Scientist, SimulaMet} \par
Conducted interdisciplinary research in the application of AI in medicine and education, with a focus on algorithmic transparency.
Worked on projects to integrate AI technologies in practical healthcare solutions, enhancing patient outcomes and system efficiencies.
Published $76$ papers at reputable conferences and journal, leading to over $1,600$ citations. Organized $7$ challenges and $4$ workshops related to machine learning, gathering several hundreds of participants.
%
\entry*[2023 -- present]%
\textbf{CTO, Innsikt.AI} \par
\begin{compactitem}
\item Heading development, strategy and innovation, focusing on virtual child avatars for police training.
\item Enhanced the interviewing skills for sensitive cases involving abused children, resulting in a 50\% increase in effective communication tactics as reported by trainee feedback.
\item Designed and implemented the initial platform, leading to a 30\% growth in client base within the first six months.
\item Enhanced LLM algorithms, leading to a 140\% increase in user retention and a 60\% improved learning efficiency.
\item Used VR technologies to create training scenarios, resulting in a 40\% increase in training engagement and a 25\% improvement in training outcome assessments.
\vspace{-12pt}
\end{compactitem}
%
\entry*[2023 -- present]%
\textbf{Associated Professor, OsloMet} \par
Focusing on machine learning solutions for musculoskeletal disorders.
Responsible for student supervision, development of novel machine learning algorithms, and conducting influential academic research.
%
\entry*[2022 -- 2023]%
\textbf{Data Scientist, ForzaSys} \par
Designed and implemented algorithms for automated clipping and highlight generation in soccer matches.
Developed software for detecting and preventing match-fixing, enhancing the integrity of sports analytics.
%
\entry*[2017 -- 2018]%
\textbf{Front-End Developer, DHIS2} \par
Optimized table rendering processes, enabling the handling of larger tables with up to 10$\times$ more data while achieving a 4$\times$ increase in application performance and a 50\% reduction in load times, markedly enhancing user experience. Enabled efficient management and access of over 10 TB of data, facilitating large-scale data operations."
%
\entry*[2014 -- 2016]%
\textbf{Full-Stack Developer, Axios AS} \par
Involved in the end-to-end development and design of loan management software for a US-based mortgage institution, ensuring compliance with industry standards.
%
\end{rubric}