\begin{rubric}{Selected Projects}
%
\entry*[2023]%
\textbf{EndoNet, American Society for Gastrointestinal Endoscopy} Engineered a robust system for the acquisition and annotation of colonoscopy data from multiple healthcare centers across the United States.
%
\entry*[2023]%
\textbf{VALIDATE, SimulaMet} Contributed the work packages related to Trustworthy AI and Clinical Model Development in the VALIDATE project for the European Union.
%
\entry*[2022]%
\textbf{Match-Fixing, Unibet and SEF} Worked with SEF and Unibet in the design and implementation of a Next.js-based application geared towards detecting match-fixing in soccer matches.
%
\entry*[2020]%
\textbf{Smittestopp, Simula} Contributed to the first version of the Smittestopp application as a member of the data science team. Responsibilities included trajectory visualizing, contact events, and classifying modes of transport.
%
\entry*[2019]
\textbf{Gastrointestinal AI, Augere} Partnered with Augere AS to construct datasets and build AI solutions to detect of gastrointestinal diseases. Models were implemented in Python using TensorFlow and PyTorch.
%
\entry*[2018]%
\textbf{Fish Feeding, Spillfree Analytics} Designed and implemented deep learning-based algorithms in TensorFlow for fish detection and classification to automate fish feeding procedures.
%
\entry*[2017]%
\textbf{Data Store Application, DHIS2} Developed a React-based application to manage data within the DHIS2 ecosystem. The application was integrated into the official DHIS2 platform, leading to part-time employment.
%
\entry*[2017]%
\textbf{Subscription Application, DNB} Created a React-based financial analytics application that analyzes bank transactions to provide users with an organized overview of daily, weekly, and yearly recurring expenses.
\end{rubric}