\begin{rubric}{Experience}
%
\entry*[2021 -- present]%
\textbf{Research Scientist, SimulaMet} Engaged in interdisciplinary research exploring the applicability of artificial intelligence in fields such as medicine and education, with a specialized focus on ensuring algorithmic transparency.
%
\entry*[2023 -- present]%
\textbf{CTO, Innsikt.AI} Serving as the Chief Technology Officer at a cutting-edge startup, spearheading the development of virtual child avatars for advanced police training modules concerning interviews with abused children.
%
\entry*[2023 -- present]%
\textbf{Associated Professor, OsloMet} Working on machine learning-based interventions for musculoskeletal disorders. Tasks include student supervision, development and implementation of novel machine learning algorithms, and academic research.
%
\entry*[2023 -- present]%
\textbf{Lecturer, BI Norwegian Business School} Teaching a graduate-level course on big data and data science, with a focus on practical applications in business contexts.
%
\entry*[2022 -- 2023]%
\textbf{Data Scientist, ForzaSys} Contributed to the design and implementation of algorithms for the automated clipping and highlight generation of soccer matches. Played a key role in software development efforts aimed at the detection and prevention of match-fixing activities.
%
\entry*[2019 -- 2020]%
\textbf{Lecturer, Kristiania University College} Delivered lectures in both introductory computer science and machine learning courses, incorporating active learning strategies to improve student comprehension and engagement.
%
\entry*[2017 -- 2018]%
\textbf{Front-End Developer, DHIS2} Focused on performance optimization of table rendering processes and contributed to the development of applications geared toward efficient data access and management.
%
\entry*[2014 -- 2016]%
\textbf{Full-Stack Developer, Axios AS} Involved in the end-to-end development and design of loan management software for a US-based mortgage institution, ensuring compliance with industry standards.
%
\end{rubric}