\begin{rubric}{Selected Projects}
%
\entry*[2023]%
\textbf{EndoNet, American Society for Gastrointestinal Endoscopy} Engineered a robust system for the acquisition and annotation of colonoscopy data from multiple healthcare centers across the United States. The platform aims to establish a comprehensive dataset to serve as a benchmark for future AI solutions in the field of gastrointestinal care.
%
\entry*[2023]%
\textbf{VALIDATE, SimulaMet} Contributed the work packages related to Trustworthy AI and Clinical Model Development.
%
\entry*[2022]%
\textbf{Match-Fixing, Unibet and SEF} Worked with SEF and Unibet in the design and implementation of a web-based application geared towards detecting match-fixing in soccer matches. The software features intricate statistics and data visualization modules to identify potential fraudulent activities. The application was developed using Next.js (front-end and back-end).
%
\entry*[2020]%
\textbf{Smittestopp, Simula} Contributed to the first version of the Smittestopp application as a member of the data science team. Responsibilities included visualizing user trajectories, validating contact events, and devising algorithms for the classification of different modes of transport. Everything was implemented in Python.
%
\entry*[2019]%
\textbf{Gastrointestinal AI, Augere AS} Partnered with Augere AS to construct datasets and AI solutions that facilitate the automatic detection of gastrointestinal diseases, thereby streamlining diagnostic processes. Models were implemented in Python using TensorFlow and PyTorch.
%
\entry*[2018]%
\textbf{Fish Feeding, Spillfree Analytics} Designed and implemented algorithms for fish detection and classification with the objective of automating feeding procedures in aquaculture. The algorithms were developed in Python using TensorFlow and PyTorch.
%
\entry*[2017]%
\textbf{Data Store Application, DHIS2} Developed a web application to manage data storage within the DHIS2 ecosystem at the University of Oslo. The application was subsequently integrated into the official DHIS2 platform, leading to part-time employment. The app was implemented in pure JavaScript.
%
\entry*[2017]%
\textbf{Subscription Application, DNB} Created a financial analytics application that scrutinizes nettbank transactions to provide users with an organized overview of daily, weekly, and yearly recurring expenses. The app also includes social features to share subscriptions with friends via Facebook. The app was developed using a React and Redux stack. There was no back-end, only DNB's internal APIs.
%
\end{rubric}