\begin{rubric}{Master Student Supervision}

    \entry*[2023]%
    \textbf{Lars Hoel} \par
    Thesis: "Using Soccer Athlete GPS Monitoring Data to Visualize and Predict Features" \par
    Mentored in analyzing and visualizing GPS monitoring data to derive actionable insights in sports performance.
    %
    \entry*[2023]%
    \textbf{Robin Rognerud} \par
    Thesis: "AI-based clipping of booking events in soccer" \par
    Oversaw the development of AI algorithms for enhancing the analysis of soccer game dynamics.
    %
    \entry*[2023]%
    \textbf{Ole Algoritme} \par
    Thesis: "Transforming Facial Landmarks for Virtual Avatar Facial Animation" \par
    Guided research in the application of machine learning for creating realistic facial animations in virtual avatars.
    %
    \entry*[2023]%
    \textbf{Mathias Menkerud Sagbakken} \par
    Thesis: "Using Machine Learning to Predict Elite Female Athletes' Readiness to Play in Soccer" \par
    Supported innovative research in predicting athletic performance and readiness using machine learning models.
    %
    \entry*[2023]%
    \textbf{Anna Linnea Jarmann} \par
    Thesis: "Identifying Injury Risk Factors for Elite Soccer Teams Using Survival Analysis" \par
    Advised on statistical methods for injury risk assessment in sports, contributing to the field of sports analytics and injury prevention.
    %
    \entry*[2023]%
    \textbf{Alexander Klougman Pishva} \par
    Thesis: "Exploring the Potential of Diffusion Models in Generating Synthetic Polyps" \par
    Mentored in exploring cutting-edge diffusion models for synthetic data generation, with applications in medical imaging.
    %
    \entry*[2022]%
    \textbf{Felicia Ly Jacobsen} \par
    Thesis: "Estimating Predictive Uncertainty in Gastrointestinal Image Segmentation" \par
    Oversaw research on quantifying uncertainty in AI-driven image segmentation, enhancing the reliability of diagnostic tools.
    %
    \entry*[2021]%
    \textbf{Joakim Olav Valand and Haris Kadragic} \par
    Thesis: "Machine learning-based approach for automated clipping of soccer events-Using scene boundary detection and logo detection" \par
    supervised a project focused on automating video analysis for soccer events, incorporating advanced scene and logo detection techniques.
    %
    \entry*[2021]%
    \textbf{Rabindra Khadka} \par
    Thesis: "Meta-learning for Medical Image Segmentation" \par
    Facilitated research on advanced meta-learning approaches for improving the accuracy of medical image segmentation.
    %
    \entry*[2020]%
    \textbf{Henrik Svoren} \par
    Thesis: "Emotional Mario-Using Super Mario Bros. to Train Emotional Intelligent Machines" \par
    Guided research on utilizing popular gaming frameworks to develop AI systems capable of understanding and interpreting emotions.
    %
    \entry*[2020]%
    \textbf{Espen Næss} \par
    Thesis: "Pyramidal Segmentation of Medical Images via Generative Adversarial Networks" \par
    Oversaw the development of advanced image segmentation techniques, enhancing medical imaging analysis.
    %
    \entry*[2020]%
    \textbf{Martin Kristoffer Svensen} \par
    Thesis: "Reidentifying Anonymised Data Using Machine Learning" \par
    Mentored on projects involving the ethical implications and technical methods of re-identifying anonymized data.
    %
    \entry*[2020]%
    \textbf{Lucas Georges Gabriel Charpentier} \par
    Thesis: "To prune or not to prune: Exploring the effects of nodes in neural networks" \par
    Facilitated research into neural network optimization, focusing on the impact of node pruning on network efficiency.
    %
    \entry*[2020]%
    \textbf{Olav Andre Nergård Rongved} \par
    Thesis: "Automatic event detection in soccer videos" \par
    Advised on developing algorithms for real-time event detection in sports videos, with a focus on soccer.
    %
    \entry*[2020]%
    \textbf{Oda Olsen Nedrejord} \par
    Thesis: "Artificial Video Generation for Improved Performance on Polyp Detection" \par
    Supervised a project focused on enhancing polyp detection in medical videos using artificial video generation techniques.
    %
    \entry*[2019]%
    \textbf{Mathias Kirkerød} \par
    Thesis: "Unsupervised preprocessing of medical imaging data with generative adversarial networks" \par
    Supported exploration into unsupervised learning methods for pre-processing medical images, contributing to the field of automated diagnostics.
    %
    \entry*[2019]%
    \textbf{Edvarda Regine Winlund Eriksen} \par
    Thesis: "A machine learning approach to improve consistency in user-driven medical image analysis" \par
    Guided the student in applying machine learning techniques to standardize and improve the reliability of user-driven image analysis.
    %
    \entry*[2019]%
    \textbf{Marius Alexander Sandberg} \par
    Thesis: "Music and Sport: An Explorative Study using Unsupervised Machine Learning" \par
    Led an interdisciplinary project merging sports analytics with musicology through machine learning techniques.
\end{rubric}