\begin{rubric}{Teaching}
\entry*[2023]%
\textbf{Master Course Instructor, Big Data Curation, Pipelines, and Management (GRA 4157), BI Norwegian Business School} \par
Led and instructed the undergraduate course "TK1101 – Digital Technology."
Focused on imparting foundational knowledge in digital technologies to technology majors.
Developed and delivered lectures, coursework, and assessments, guiding students through practical and theoretical aspects of the subject.
%
\entry*[2020]%
\textbf{Bachelor Course Instructor, Digital Technology (TK1101), Kristiania University College} \par
Led and instructed the undergraduate course "TK1101 – Digital Technology."
Focused on imparting foundational knowledge in digital technologies to technology majors.
Developed and delivered lectures, coursework, and assessments, guiding students through practical and theoretical aspects of the subject.
%
\entry*[2019]%
\textbf{Examination Assessor, Data Science (INS301), Kristiania University College} \par
Served as an examination assessor for the "INS301 – Data Science" course.
Responsible for evaluating student submissions, ensuring academic integrity, and providing fair and constructive feedback.
Contributed to the continuous improvement of examination standards and practices.
%
\entry*[2019]%
\textbf{Bachelor Course Instructor, Machine Learning (TEK300), Kristiania University College} \par
Conducted the undergraduate course "TEK300 – Machine Learning."
Covered key concepts and applications of machine learning, emphasizing practical skills and theoretical understanding.
Facilitated student learning through interactive lectures, project supervision, and comprehensive evaluations.
%
\entry*[2019]%
\textbf{Master Course Instructor, Emerging Technologies (MS340), Kristiania University College} \par
Taught the master-level course "MS340 – Emerging Technologies."
Focused on advanced topics in applied computer science, including recent technological advancements and their applications.
Engaged postgraduate students in critical discussions, research-based learning, and hands-on projects.
%
\entry*[2019]%
\textbf{Examination Assessor, Introduction to Operating Systems (INF1060), University of Oslo} \par
Assumed the role of examination assessor for "INF1060 – Introduction to Operating Systems."
Assessed student knowledge and understanding of operating systems, ensuring accurate and fair evaluation of their competencies.
Played a key role in maintaining the academic quality and standards of the university’s computer science program.
\end{rubric}